A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-18 FMCAD2021/6_impl_exp.tex
modify stringhash table

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% Merge bound and unbound 
\begin{table*}[]
    \label{table:arithmetic}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on arithmetic benchmark}
    \centering
    \begin{tabular}{cc|cc|cc|cc}
        \multicolumn{1}{l}{} &  & \multicolumn{2}{c|}{Z3} & \multicolumn{2}{c|}{CVC4} & \multicolumn{2}{c}{MySolver} \\
        \multicolumn{1}{l}{} &  & number & avg & number & avg & number & avg \\ \hline
        \multirow{4}{*}{2-3-3-4} & SAT & 56 & 0.4 & 42 & 2.3 & 64 & 0.4 \\
         & UNSAT & 69 & \textless{}0.1 & 72 & \textless{}0.1 & 89 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 47 & 9.5 \\
         & TIMEOUT & 75 &  & 86 &  & 0 &  \\ \hline
        \multirow{4}{*}{3-4-4-5} & SAT & 33 & 1.4 & 25 & 2.9 & 52 & 3.3 \\
         & UNSAT & 59 & \textless{}0.1 & 60 & \textless{}0.1 & 88 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 1 & 54.0 \\
         & TIMEOUT & 108 &  & 115 &  & 59 &  \\ \hline
        \multirow{4}{*}{4-5-5-6} & SAT & 35 & 1.8 & 19 & 6.6 & 47 & 22.4 \\
         & UNSAT & 36 & 0.3 & 39 & 0.4 & 72 & 0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 0 &  \\
         & TIMEOUT & 129 &  & 142 &  & 81 & 
        \end{tabular}
\end{table*}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table*}[]
    \label{table:string}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on string hash function benchmark}
    \begin{tabular}{c|c|ccc|ccc|ccc}
                                                       &     & \multicolumn{3}{c|}{Z3} & \multicolumn{3}{c|}{CVC4} & \multicolumn{3}{c}{MySolver}       \\
    PATTERN                                            & $\ell_{10}(m_1)$   & SAT  & UNSAT  & TIMEOUT & SAT   & UNSAT  & TIMEOUT  & SAT & UNSAT & TIMEOUT              \\ \hline
    \multirow{5}{*}{12345(a)*(b)*}                     & 2   & 5    &        & 20      & 23    &        & 2        & 24  & 1     & 0                    \\
                                                       & 3   & 0    &        & 25      & 4     &        & 21       & 10  & 14    & 1                    \\
                                                       & 4   & 0    &        & 25      & 1     &        & 24       & 2   & 22    & 1                    \\
                                                       & 5   & 0    &        & 25      & 1     &        & 24       & 1   & 23    & 1                    \\
                                                       & total & 5    &        & 95      & 29    &        & 71       & 37  & 60    & 3                    \\ \hline
    \multirow{5}{*}{12345(a)*(b)*6789}                 & 2   & 10   &        & 15      & 18    &        & 7        & 24  & 1     & 0                    \\
                                                       & 3   & 1    &        & 24      & 8     &        & 17       & 10  & 15    & 0                    \\
                                                       & 4   & 0    &        & 25      & 3     &        & 22       & 3   & 22    & 0                    \\
                                                       & 5   & 0    &        & 25      & 0     &        & 25       & 0   & 25    & 0                    \\
                                                       & total & 11   &        & 89      & 29    &        & 71       & 37  & 63    & 0                    \\ \hline
    \multirow{5}{*}{(a)*(b)*6789}                      & 2   & 14   &        & 11      & 23    &        & 2        & 22  & 3     & 0                    \\
                                                       & 3   & 4    &        & 21      & 6     & 1      & 18       & 15  & 10    & 0                    \\
                                                       & 4   & 0    &        & 25      & 1     &        & 24       & 3   & 22    & 0                    \\
                                                       & 5   & 0    &        & 25      & 0     &        & 25       & 1   & 24    & 0                    \\
                                                       & total & 18   &        & 82      & 30    & 1      & 69       & 41  & 59    & 0                    \\ \hline\hline
    \multirow{5}{*}{12345$(\Sigma_{num})^*$}     & 2   & 25   &        & 0       & 25    &        & 0        & 25  &       &                      \\
                                                       & 3   & 25   &        & 0       & 25    &        & 0        & 25  &       &                      \\
                                                       & 4   & 23   &        & 2       & 25    &        & 0        & 25  &       &                      \\
                                                       & 5   & 9    &        & 16      & 25    &        & 0        & 25  &       &                      \\
                                                       & total & 82   &        & 18      & 100   &        & 0        & 100 &       &                      \\ \hline
    \multirow{5}{*}{12345$(\Sigma_{num})^*$6789} & 2   & 25   &        & 0       & 15    &        & 10       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 3   & 23   &        & 2       & 1     &        & 24       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 4   & 9    &        & 16      & 1     &        & 24       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 5   & 3    &        & 22      & 0     &        & 25       & 25  &       &                      \\
                                                       & total & 60   &        & 40      & 17    &        & 83       & 100 &       &                      \\ \hline
    \multirow{5}{*}{$(\Sigma_{num})^*$6789}      & 2   & 25   &        & 0       & 19    &        & 6        & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 3   & 25   &        & 0       & 4     &        & 21       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 4   & 16   &        & 9       & 4     &        & 21       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 5   & 2    &        & 23      & 0     &        & 25       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & total & 68   &        & 32      & 27    &        & 73       & 100 &       &                     
    \end{tabular}
\end{table*}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% Merge bound and unbound 
\begin{table*}[]
    \label{table:arithmetic}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on arithmetic benchmark}
    \centering
    \begin{tabular}{cc|cc|cc|cc}
        \multicolumn{1}{l}{} &  & \multicolumn{2}{c|}{Z3} & \multicolumn{2}{c|}{CVC4} & \multicolumn{2}{c}{$\paexp$-solver} \\
        \multicolumn{1}{l}{} &  & number & avg & number & avg & number & avg \\ \hline
        \multirow{4}{*}{2-3-3-4} & SAT & 56 & 0.4 & 42 & 2.3 & 64 & 0.4 \\
         & UNSAT & 69 & \textless{}0.1 & 72 & \textless{}0.1 & 89 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 47 & 9.5 \\
         & TIMEOUT & 75 &  & 86 &  & 0 &  \\ \hline
        \multirow{4}{*}{3-4-4-5} & SAT & 33 & 1.4 & 25 & 2.9 & 52 & 3.3 \\
         & UNSAT & 59 & \textless{}0.1 & 60 & \textless{}0.1 & 88 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 1 & 54.0 \\
         & TIMEOUT & 108 &  & 115 &  & 59 &  \\ \hline
        \multirow{4}{*}{4-5-5-6} & SAT & 35 & 1.8 & 19 & 6.6 & 47 & 22.4 \\
         & UNSAT & 36 & 0.3 & 39 & 0.4 & 72 & 0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 0 &  \\
         & TIMEOUT & 129 &  & 142 &  & 81 & 
        \end{tabular}
\end{table*}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table*}[]
    \label{table:string}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on string hash function benchmark}
    \centering
    \begin{tabular}{cc|cc|cc|cc|cc}
        &  & \multicolumn{2}{c|}{Z3} & \multicolumn{2}{c|}{CVC4} & \multicolumn{2}{c|}{Trau} & \multicolumn{2}{c}{mysovler} \\
       PATTERN &  & number & time & number & time & number & time & number & time \\ \hline
       \multirow{3}{*}{12345(a)+(b)+} & SAT & 5 & 14.0 & 29 & 8.5 & 3 & \textless{}0.1 & 37 & 9.9 \\
        & UNSAT & 0 &  & 0 &  & 60 & 1.3 & 60 & 47.2 \\
        & FAIL & 95 &  & 71 &  & 32 &  & 3 &  \\ \hline
       \multirow{3}{*}{12345(a)+(b)+6789} & SAT & 11 & 13.0 & 29 & 12.0 & 0 &  & 37 & 10.6 \\
        & UNSAT & 0 &  & 0 &  & 63 & 1.2 & 63 & 50.0 \\
        & FAIL & 89 &  & 71 &  & 37 &  & 0 &  \\ \hline
       \multirow{3}{*}{(a)+(b)+6789} & SAT & 18 & 24.0 & 30 & 9.3 & 2 & \textless{}0.1 & 41 & 16.1 \\
        & UNSAT & 0 &  & 1 & 4.0 & 59 & 2.5 & 59 & 45.8 \\
        & FAIL & 82 &  & 69 &  & 39 &  & 0 &  \\ \hline
       \multirow{3}{*}{12345(\textbackslash{}Sigma)*} & SAT & 82 & 8.7 & 100 & 2.2 & 28 & 5.9 & 100 & 18.5 \\
        & UNSAT & 0 &  & 0 &  & 0 &  & 0 &  \\
        & FAIL & 18 &  & 0 &  & 72 &  & 0 &  \\ \hline
       \multirow{3}{*}{12345(\textbackslash{}Sigma)*6789} & SAT & 60 & 9.3 & 17 & 7.8 & 3 & 0.3 & 100 & 16.0 \\
        & UNSAT & 0 &  & 0 &  & 0 &  & 0 &  \\
        & FAIL & 40 &  & 83 &  & 97 &  & 0 &  \\ \hline
       \multirow{3}{*}{(\textbackslash{}Sigma)*6789} & SAT & 68 & 5.5 & 27 & 13.0 & 24 & 9.0 & 100 & 15.7 \\
        & UNSAT & 0 &  & 0 &  & 0 &  & 0 &  \\
        & FAIL & 32 &  & 73 &  & 76 &  & 0 & 
       \end{tabular}
\end{table*}
